### 2020-04-20 final_report/methodology.tex
add one more paragraph on metrics

To prevent undesirable bias in results due to training set selection, metrics
related to both properties are collected using $k$-fold cross-validation with a
standard choice of $k=5$. Herein, a sample set is subdivided into 5 disjoint
folds which are repeatedly interpreted as training and testing sets, maintaining
a constant ratio of samples between the two. In each such interpretation experiments are
repeated, and the overall value of each metric of interest is reported as the mean
across all folds.

\Cref{tbl:metrics} provides exhaustive list and description of
regression performance and evaluation time metrics recorded in the experiments.

\begin{table}[h]
	\centering
	\begin{tabular}{lll}
	\toprule
	Regression performance metrics	& Mathematical formulation / description & Ideal value \\
	\midrule
	Mean absolute error	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0 [TBR] \\
	$R^2$ ratio (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 [rel.] \\
	Adjusted $R^2$ ratio	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 [rel.] \\
	Standard error of regression	& $\text{StdDev}_{i=1}^N\left( |y^{(i)} -
	\hat{y}^{(i)}| \right) $	 & 0 [TBR] \\
	\midrule
	Evaluation time metrics	& {} & {} \\
	\midrule
	Mean sample training time	& $(\text{wall training time of $\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
	Mean sample prediction time	& $(\text{wall evaluation time of $\hat{f}(x)$})/N$	& 0 [ms] \\
	\bottomrule
	\end{tabular}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

>>>>

\Cref{tbl:metrics} provides exhaustive list and description of metrics recorded
in the experiments. For regression performance analysis, we include a selection
of absolute metrics to assess the approximation capability of surrogates, and set
practical bounds on the expected accuracy of their predictions. In addition, we also track
relative measures that are better-suited for model comparison between works as
they maintain invariance with respect to the domain and image space.

\begin{table}[h]
	\centering
	\begin{tabular}{lll}
	\toprule
	Regression performance metrics	& Mathematical formulation / description & Ideal value \\
	\midrule
	Mean absolute error (MAE)	& $\sum_{i=1}^N |y^{(i)}-\hat{y}^{(i)}|/N$ & 0
	[TBR] \\
	Standard error of regression $S$	& $\text{StdDev}_{i=1}^N\left( |y^{(i)} -
	\hat{y}^{(i)}| \right) $	 & 0 [TBR] \\
	$R^2$ ratio (coefficient of determination)	& $1-\sum_{i=1}^N \left(y^{(i)}-\hat{y}^{(i)} \right)^2 /
	\sum_{i=1}^N \left( y^{(i)}-\overline{y} \right)^2 $ & 1 [rel.] \\
	Adjusted $R^2$ ratio	& $1-(1-R^2)(N-1)/(N-P-1)$	& 1 [rel.] \\
	\midrule
	Evaluation time metrics	& {} & {} \\
	\midrule
	Mean sample training time	& $(\text{wall training time of
	$\hat{f}(x)$})/N_0$ 	& 0 [ms] \\
	Mean sample prediction time	& $(\text{wall evaluation time of
	$\hat{f}(x)$})/N$	& 0 [ms] \\
	\bottomrule
	\end{tabular}
	\caption{Metrics recorded in supervised learning experiments. In
	formulations, we work with training set of size $N_0$ and testing set of
size $N$, TBR values $y^{(i)}=f(x^{(i)})$ and $\hat{y}^{(i)}=\hat{f}(x^{(i)})$
denote images of the $i$th testing sample in the expensive model and the surrogate
respectively. Furthermore, the mean $\overline{y}=\sum_{i=1}^N y^{(i)}/N$ and $P$ is the
number of input features.}
	\label{tbl:metrics}
\end{table}

To prevent undesirable bias in results due to training set selection, all metrics
collected in the scheme of $k$-fold cross-validation with a standard choice of
$k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
repeatedly interpreted as training and testing sets, maintaining a constant
ratio of samples between the two. In each such interpretation experiments are
repeated, and the overall value of each metric of interest is reported as the
mean across all folds.
